gss marriage politics analysis

### 2023-04-19 outputs/paper/paper.qmd
added variable description and measurement tables

---
title: "gss marriage politics analysis"
subtitle: "subtitle"
author: 
  - First author
  - Another author
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_political_affiliation_gss_analysis.git"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}

@@

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

@@

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

Talk way more about it.

@@

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

>>>>

---
title: "gss marriage politics analysis"
subtitle: "subtitle"
author: 
  - Chloe Thierstein
thanks: "Code and data are available at: https://github.com/cthierst/marital_status_political_affiliation_gss_analysis.git"
date: "April 20, 2023"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
toc: TRUE
number-sections: TRUE
bibliography: references.bib
---

```{r}
#| include: false

#### Load Library ####
library(tidyverse)
library(janitor)
library(ggplot2)
library(RColorBrewer)
library(kableExtra)
library(knitr)
library(dplyr)
library(here)
library(RColorBrewer)
library(kableExtra)
library(patchwork)
library(readr)
library(here)

#### Import cleaned_gss_2021.csv ####
cleaned_gss_2021 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2021.csv"))

cleaned_gss_2018 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2018.csv"))

cleaned_gss_2016 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2016.csv"))

cleaned_gss_2014 <-
  read.csv(here::here("inputs/clean_data/cleaned_gss_2014.csv"))
```

@@

## Data Management

This paper uses the R statistical programming language [@citeR], along with several packages, tidyverse [@citetidy]

## Source

## Sampling

## Key Features

```{r}
#| include: false

#### Create Variable Description Tibble ####

variable_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Description" = c(
      "Self-ascribed belonging to the Republican, Democratic, or Indepedent parties",
    "Self-ascribed placement on a Likert scale from 'extremely liberal to extremely conservative'",
    "Marital status of respondent",
    "Self-ascribed sex of respondent",
    "Generational cohort that respondent belongs to "
    )
  )

@@

```{r}
#| echo: false
#| warning: false
#| label: tbl-1
#| tbl-cap: "Variable Descriptions"
#### Add Variable Table ####
variable_table |>
  kable(booktabs = TRUE) |>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

```{r}
#| include: false
#### Create Variable Description Tibble ####

variable_measure_table <-
  tibble(
    "Variable" = c(
      "partyid",
      "polviews",
      "marital",
      "sex",
      "cohort"
    ),
    "Variable Measurement" = c(
      "Strong Democrat, Not Very Strong Democrat, Independent (Close to Democrat), Independent (Neither), Independent (Close to Republican), Not Very Strong Republican, Strong Republican",
      "Extremely Liberal, Liberal, Slightly Liberal, Moderate, Slightly Conservative, Conservative, Extremely Conservative",
      "Married, Never Married, Separated, Divorced, Widowed",
      "Female, Male",
      "Post-War, Boomer, Gen X, Millenial, Gen Z"
    )
  )
```

```{r}
#| echo: false
#| warning: false
#| label: tbl-2
#| tbl-cap: "Variable Measurements"
#### Add Variable Table ####
variable_measure_table |>
  kable(booktabs = TRUE) |>
  column_spec(2, width = "41em")|>
  kable_styling(font_size = 9, latex_options = "hold_position")
```

## Bias and Ethics

@@

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```
We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

@@
